Towards Proof-Reconstruction of Problems in Classical Propositional Logic in Agda

### 2017-07-27 paper/main.tex
Working on the introduction.

% first the title is needed
\title{Towards Proof-Reconstruction of Problems in Classical Propositional Logic}

% a short form should be given in case it is too long for the running head
\titlerunning{Towards Proof-Reconstruction of Problems in Classical Propositional Logic}

@@

\section{Introduction}
Proof reconstruction is a hard labor, it depends on the integration of two complex systems. On one hand, we have the automatic theorem provers (henceforth ATPs), these are programs designed to answer automatically if a statement, the conjecture, is a theorem, is counter-feasible or is unknown based on a set of hypothesis. Provers often deal with problems in First-Order Logic with or without equality, High-Order Logic, Intuitionistic Logic, and other logics or background theories.

For proof reconstruction, we are interested in ATP tools that can deliver proof objects in a consistent format to work with, that is, a full   script  describing  step-by-step the table of the derivation to get the proof. Unfortunately, just a few of the ATPs can give us such a proof object. For problems in Classical Propositional Logic (henceforth CPL), from a list of at least forty\footnote{ATPs available in the website  \texttt{SystemOnTPTP} from the TPTP World} ATPs, just a few can deliver proofs (e.g. \verb!CVC4!~\cite{Barrett2011}, \verb!SPASS!~\cite{Weidenbach2009}, \verb!Waldmeister!~\cite{hillenbrand1997}) and a little bit less deliver proofs in the TSTP file format (e.g. \verb!E!~\cite{Schulz:AICOM-2002}, \verb!Metis!~\cite{hurd2003first}, \verb!Vampire!~\cite{Riazanov1999}, \verb!Z3!).

@@

\subsection*{Related Work.}\label{Related Work}
\par
\verb!Sledgehammer! is a tool for \verb!Isabelle! proof assistant~\cite{paulson1994isabelle} that provides a full integration of automatic theorem provers including ATPs (see, for example, \cite{meng2006automation} and~\cite{blanchette2013extending}) and SMT solvers (see, for example,~\cite{blanchette2013extending}) with \verb!Isabelle/HOL!~\cite{nipkow2002isabelle}, the specialization of \verb!Isabelle! for Higher-Order Logic.

@@

\verb!SMTCoq! \cite{armand2011} is a tool for the \verb!Coq! proof assistant \cite{coqteam} which provides a certified checker for proof witness coming from the SMT solver \verb!veriT! \cite{bouton2009} and adds a new tactic named verit, that calls \verb!veriT! on any \verb!Coq! goal.

>>>>

% first the title is needed
\title{Towards Proof-Reconstruction of Problems in Classical Propositional Logic
in Agda}

% a short form should be given in case it is too long for the running head
\titlerunning{Towards Proof-Reconstruction of Problems in Classical
  Propositional Logic in Agda}

@@

\section{Introduction}
Proof reconstruction is a hard labor, it integrates two
complex systems. On one hand, we have the automatic theorem provers (henceforth
ATPs) that depending on the specification logic and background theories exist
many alternatives. They are SAT solvers (e.g. \verb!zChaff!~\cite{Moskewicz2001} and \verb!MiniSat!~\cite{Een2004}) to prove unsatisfiability of CNF formulas,
QBF solvers (e.g.~\verb!GhostQ!~\cite{Klieber2014} and ~\verb!DepQBF!~\cite{Lonsing2017}) to prove satisfiability and invalidity of quantified Boolean
formulas, SMT solvers (e.g \verb!CVC4!~\cite{Barrett2011}, \verb!veriT!~\cite{bouton2009}, \verb!Z3!~\cite{DeMoura2008}) to
prove unsatisfiability of formulas from first-order logic with theories,  and
finally, the ATPs to prove validity of formulas from first-order logic with
equality (e.g.~\verb!E!~\cite{Schulz:AICOM-2002},~\verb!Gandalf!~\cite{Tammet1997},~\verb!leanCoP!~\cite{Otten2008},~\verb!Metis!~\cite{hurd2003first},~\verb!SPASS!~\cite{Weidenbach2009} and ~\verb!Vampire!~\cite{Riazanov1999}),
high-order logic (e.g.~\verb!Leo-II!,~\verb!Satallax!), intuitonistic logic
(e.g.~\verb!ileanCoP!~\cite{Otten2008},~\verb!JProver!~\cite{Schmitt2001},~\verb!Gandalf!~\cite{Tammet1997}), among others.

For proof reconstruction, we are interested in ATP tools that can deliver proof
objects in a consistent format to work with, that is, a full script describing
step-by-step the table of the derivation to get the actual proof. Unfortunately,
just a few of the ATPs generate in their outputs a proof object.

For problems in classical propositional logic (henceforth CPL), from a list of
at least forty\footnote{ATPs available in the website  \texttt{SystemOnTPTP}
  from the TPTP World} ATPs, just a few deliver proofs (e.g.
\verb!CVC4!~\cite{Barrett2011}, \verb!SPASS!~\cite{Weidenbach2009},
\verb!Waldmeister!~\cite{hillenbrand1997}) and a little bit less proofs in file
format like TSTP (e.g. \verb!E!~\cite{Schulz:AICOM-2002}, \verb!Metis!~\cite{hurd2003first}, \verb!Vampire!~\cite{Riazanov1999}, \verb!Z3!).

@@

\subsection*{Related Work.}\label{Related Work}
\par
\verb!Sledgehammer! is a tool for \verb!Isabelle! proof
assistant~\cite{paulson1994isabelle} that provides a full integration of
automatic theorem provers including ATPs (see, for example,
\cite{meng2006automation}, ~\cite{blanchette2013extending} and \cite{Fleury2014}) and SMT solvers (see, for
example,~\cite{blanchette2013extending},~\cite{bohme2010} and \cite{Fleury2014}) with \verb!Isabelle/HOL!~\cite{nipkow2002isabelle}, the specialization of \verb!Isabelle! for Higher-Order Logic.

@@

\verb!SMTCoq! (see \cite{armand2011} and \cite{Ekici2017} for more details) is a tool for the \verb!Coq! proof assistant \cite{coqteam} which provides a certified checker for proof witness coming from the SMT solver \verb!veriT! \cite{bouton2009} and adds a new tactic named verit, that calls \verb!veriT! on any \verb!Coq! goal.
